---
title: "<b><i>CMAP</i></b> | Commercial Services Vehicle Model | `r paste(SCENARIO_NAME, 'Scenario')`"
date: "`r format(SCENARIO_RUN_START, '%Y-%m-%d')`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: yeti
    css: "ReportDashboardStyles.css"
editor_options: 
  chunk_output_type: console
---

```{r ggplot_Theme}
theme_db <- theme_bw() + theme(plot.margin = unit(c(10,10,20,10),"pt")) 
```

```{r Map_Settings}
map_type <- "CartoDB.Positron"
```

Overview {data-icon="fa-home"}
============================================

Highlights {data-width=150}
--------------------------------------------

**Overview**

Firms, employment, and commercial vehicle trip totals for the CMAP region

```{r highlights_build_firm_sim, results='asis', eval=SCENARIO_DB_FIRMSYN}
highlights_firm_sim <- knitr::knit_child('highlights_firm_sim.Rmd',
                              envir = environment(),
                              quiet = TRUE)
cat(unlist(highlights_firm_sim), sep = '\n')
```

```{r highlights_build_cv_sim, results='asis', eval=SCENARIO_DB_CVTM}
highlights_cv_sim <- knitr::knit_child('highlights_cv_sim.Rmd',
                              envir = environment(),
                              quiet = TRUE)
cat(unlist(highlights_cv_sim), sep = '\n')
```

```{r highlights_build_tt, results='asis', eval=SCENARIO_DB_TT}
highlights_tt <- knitr::knit_child('highlights_tt.Rmd',
                              envir = environment(),
                              quiet = TRUE)
cat(unlist(highlights_tt), sep = '\n')
```


Summary {data-width=200, .tabset}
--------------------------------------------

### Introduction

<style>
div#introduction.section.level3.chart-wrapper.chart-wrapper-flex {
  flex: 70% !important;
  font-size: 12px !important;
}
div#about-this-document.section.level3.chart-wrapper.chart-wrapper-flex {
  flex: 30% !important;
  font-size: 12px !important;
}
</style>

The CMAP Commercial Services Vehicle Model simulates truck trips within the 21 county CMAP model region. This dashboard presents the results from a scenario run of the model, indicated by the scenario name and year indicated in the header above.

The model comprises two components; the outputs from each one are shown in the other tabs of the dashboard:

1. Firm Synthesis Model: a list of businesses establishments in the CMAP region
2. Commercial Vehicle Touring Model: simulation of commercial vehicle travel within the CMAP region

### About this Document

This stand-alone interactive dashboard is viewable from most modern Internet browsers. All of the data, charts, and maps viewable in this dashboard are embedded directly into the HTML file, so users are encouraged to share the scenario results with others via this document. An Internet connection is necessary for the best user experience, but is not required.

Users may navigate to different areas of the dashboard using the navigation bar at the top of the page, and may interact directly with most tables, charts, and maps.

This document is best viewed using the most recent versions of the following web browsers:

* [Google Chrome](https://www.google.com/chrome/browser/desktop/)
* [Mozilla Firefox](https://www.mozilla.org/en-US/firefox/new/)
* Microsoft Edge (Must be running Windows 10)

Summary Results {data-width=300, .tabset}
--------------------------------------------

### Trips

```{r Summary_Table_Trips}

# Summarize the tmh_vtods table for trips
dat <- add_totals(dcast.data.table(tmh_vtods[,.(Trips = sum(Trips)), 
                                         keyby = .(Vehicle, ODSegment)],
                     Vehicle ~ ODSegment,
                     fun.aggregate = sum,
                     value.var = "Trips"))

cols <- names(dat)[2:ncol(dat)]
dat[, (cols) := lapply(.SD, format, digits = 0, big.mark = ",", scientific = FALSE), .SDcols = cols]

kable(dat, escape=FALSE, align = "llrrrrr") %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```

> Units in the table is number of daily trips within, to, from, and through the CMAP region.

### Vehicle Miles Traveled

```{r Summary_Table_VMT}

# Summarize the tmh_vtods table for VMT
dat <- add_totals(dcast.data.table(tmh_vtods[,.(VMT = sum(VMT)), 
                                         keyby = .(Vehicle, ODSegment)],
                     Vehicle ~ ODSegment,
                     fun.aggregate = sum,
                     value.var = "VMT"))

cols <- names(dat)[2:ncol(dat)]
dat[, (cols) := lapply(.SD, format, digits = 0, big.mark = ",", scientific = FALSE), .SDcols = cols]

kable(dat, escape=FALSE, align = "llrrrrr") %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```

> Units in the table is vehicle miles traveled within, to, from, and through the CMAP region

### Vehicle Hours Traveled

```{r Summary_Table_VHT}

# Summarize the tmh_vtods table for VHT
dat <- add_totals(dcast.data.table(tmh_vtods[,.(VHT = sum(VHT)), 
                                         keyby = .(Vehicle, ODSegment)],
                     Vehicle ~ ODSegment,
                     fun.aggregate = sum,
                     value.var = "VHT"))

cols <- names(dat)[2:ncol(dat)]
dat[, (cols) := lapply(.SD, format, digits = 0, big.mark = ",", scientific = FALSE), .SDcols = cols]

kable(dat, escape=FALSE, align = "llrrrrr") %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```

> Units in the table is vehicle hours traveled within, to, from, and through the CMAP region.

### Average Trip Distance

```{r Summary_Table_MeanDistance}

# Summarize the tmh_vtods table for mean distance
dat_vehicle <- cbind(dcast.data.table(tmh_vtods[,.(MeanDist = sum(VMT, na.rm = TRUE)/sum(Trips, na.rm = TRUE)), 
                                         keyby = .(Vehicle, ODSegment)],
                     Vehicle ~ ODSegment,
                     fun.aggregate = sum,
                     value.var = "MeanDist"),
                     tmh_vtods[,.(Total = sum(VMT, na.rm = TRUE)/sum(Trips, na.rm = TRUE)), 
                                         keyby = .(Vehicle)][,.(Total)])

dat_total <- cbind(dcast.data.table(tmh_vtods[,.(Vehicle = "Total", MeanDist = sum(VMT, na.rm = TRUE)/sum(Trips, na.rm = TRUE)), 
                                         keyby = .(ODSegment)],
                     Vehicle ~ ODSegment,
                     fun.aggregate = sum,
                     value.var = "MeanDist"), 
                 tmh_vtods[,.(Total = sum(VMT, na.rm = TRUE)/sum(Trips, na.rm = TRUE))])

dat <- rbind(dat_vehicle,
             dat_total)

dat[is.na(dat)] <- 0
cols <- names(dat)[2:ncol(dat)]
dat[, (cols) := lapply(.SD, format, digits = 3, big.mark = ",", scientific = FALSE), .SDcols = cols]

kable(dat, escape=FALSE, align = "llrrrrr") %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```

> Units in the table is average trip distance in miles, for trips within, to, from, and through the CMAP region.

### Average Trip Time

```{r Summary_Table_MeanTime}

# Summarize the tmh_vtods table for mean time
dat_vehicle <- cbind(dcast.data.table(tmh_vtods[,.(MeanTime = sum(VHT * 60, na.rm = TRUE)/sum(Trips, na.rm = TRUE)), 
                                         keyby = .(Vehicle, ODSegment)],
                     Vehicle ~ ODSegment,
                     fun.aggregate = sum,
                     value.var = "MeanTime"),
                     tmh_vtods[,.(Total = sum(VHT * 60, na.rm = TRUE)/sum(Trips, na.rm = TRUE)), 
                                         keyby = .(Vehicle)][,.(Total)])

dat_total <- cbind(dcast.data.table(tmh_vtods[,.(Vehicle = "Total", MeanTime = sum(VHT * 60, na.rm = TRUE)/sum(Trips, na.rm = TRUE)), 
                                         keyby = .(ODSegment)],
                     Vehicle ~ ODSegment,
                     fun.aggregate = sum,
                     value.var = "MeanTime"), 
                 tmh_vtods[,.(Total = sum(VHT * 60, na.rm = TRUE)/sum(Trips, na.rm = TRUE))])

dat <- rbind(dat_vehicle,
             dat_total)

dat[is.na(dat)] <- 0
cols <- names(dat)[2:ncol(dat)]
dat[, (cols) := lapply(.SD, format, digits = 3, big.mark = ",", scientific = FALSE), .SDcols = cols]

kable(dat, escape=FALSE, align = "llrrrrr") %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```

> Units in the table is average trip travel time in minutes, for trips within, to, from, and through the CMAP region.

### Average Speed

```{r Summary_Table_MeanSpeed}

# Summarize the tmh_vtods table for mean speed
dat_vehicle <- cbind(dcast.data.table(tmh_vtods[,.(MeanSpeed = sum(VMT, na.rm = TRUE)/sum(VHT, na.rm = TRUE)), 
                                         keyby = .(Vehicle, ODSegment)],
                     Vehicle ~ ODSegment,
                     fun.aggregate = sum,
                     value.var = "MeanSpeed"),
                     tmh_vtods[,.(Total = sum(VMT, na.rm = TRUE)/sum(VHT, na.rm = TRUE)), 
                                         keyby = .(Vehicle)][,.(Total)])

dat_total <- cbind(dcast.data.table(tmh_vtods[,.(Vehicle = "Total", MeanSpeed = sum(VMT, na.rm = TRUE)/sum(VHT, na.rm = TRUE)), 
                                         keyby = .(ODSegment)],
                     Vehicle ~ ODSegment,
                     fun.aggregate = sum,
                     value.var = "MeanSpeed"), 
                 tmh_vtods[,.(Total = sum(VMT, na.rm = TRUE)/sum(VHT, na.rm = TRUE))])

dat <- rbind(dat_vehicle,
             dat_total)

dat[is.na(dat)] <- 0
cols <- names(dat)[2:ncol(dat)]
dat[, (cols) := lapply(.SD, format, digits = 3, big.mark = ",", scientific = FALSE), .SDcols = cols]

kable(dat, escape=FALSE, align = "llrrrrr") %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```

> Units in the table is average trip speed in miles per hour, for trips within, to, from, and through the CMAP region.

Model Region Map and Glossary {data-width=300, .tabset}
--------------------------------------------

### Model Region and Traffic Analysis Zone (TAZ) System

```{r Model_Region_Map}
map <- leaflet() %>%
  addProviderTiles(map_type, group = "Background Map") %>%
  addLayersControl(
    overlayGroups = "Background Map", options = layersControlOptions(collapsed = FALSE)
  ) %>%
  addTAZPolygons() %>%
  addLegend(position = "bottomright", pal = colorFun, values = ~Group, data = TAZ.polys) %>%
  addPolygons(data = shp, weight = 0.5,
              opacity = 0.25, color = "grey",
              fillOpacity = 0, fillColor = "white") %>%
  addEasyButton(easyButton(
    icon = "ion-arrow-shrink",
    title = "Reset View",
    onClick = JS("function(btn, map){
                 map.setView(map._initialCenter, map._initialZoom);}"))) %>%
  htmlwidgets::onRender(JS("function(el, x){
  var map = this;
  map.whenReady(function(){
    map._initialCenter = map.getCenter();
    map._initialZoom = map.getZoom();
  });
  }"))
map %>% htmlwidgets::onRender(JS(paste0("function(el, x){
var map = this;
var corner1 = new L.LatLng(",CMAP_BBOX["y", "min"],", ",CMAP_BBOX["x", "min"],"),
    corner2 = new L.LatLng(",CMAP_BBOX["y", "max"],", ",CMAP_BBOX["x", "max"],"),
    bounds = new L.LatLngBounds(corner1, corner2);
map.fitBounds(bounds);
}")))
```

### Employment Categories

```{r n2_To_Employment_Category}
# Show table

kable(c_n2_empcats, escape=FALSE, col.names = c("Employment Category",
                                               "Employment Cateogry Description",
                                               "Employment Group")) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("striped"))

```

### CVTM Stop Activities

```{r CVTM_Stop_Activities_Descr}
# Show table
activities_table <- data.table(Activity = c("Goods", "Service", "Return", "Break/Meal", "Vehicle Service", "Other"),
                         Scheduled = c("Scheduled", "Scheduled", "Scheduled", "Non-Scheduled", "Non-Scheduled", "Non-Scheduled"),
                         Description = c("Delivery or pick-up of goods", "Service call at a customer", "Final stop of a tour returning to the start location", "Driver break or meal stop", "Driver stop to refuel or service vehicle", "Other non-scheduled stops"))

kable(activities_table, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("striped"))

```


<!-- ```{r section_build_firm_sim, results='asis', eval=SCENARIO_DB_FIRMSYN} -->
<!-- section_firm_sim <- knitr::knit_child('section_firm_sim.Rmd', -->
<!--                               envir = environment(), -->
<!--                               quiet = TRUE) -->
<!-- cat(unlist(section_firm_sim), sep = '\n') -->
<!-- ``` -->

<!-- ```{r section_build_cv_sim, results='asis', eval=SCENARIO_DB_CVTM} -->
<!-- section_cv_sim <- knitr::knit_child('section_cv_sim.Rmd', -->
<!--                               envir = environment(), -->
<!--                               quiet = TRUE) -->
<!-- cat(unlist(section_cv_sim), sep = '\n') -->
<!-- ``` -->

<!-- ```{r section_build_tt, results='asis', eval=SCENARIO_DB_TT} -->
<!-- section_tt <- knitr::knit_child('section_tt.Rmd', -->
<!--                               envir = environment(), -->
<!--                               quiet = TRUE) -->
<!-- cat(unlist(section_tt), sep = '\n') -->
<!-- ``` -->

