---
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: yeti
    css: "ReportDashboardStyles.css"
editor_options: 
  chunk_output_type: console
---

Comparison Stops {data-navmenu="Commercial Vehicle Touring Model"}
============================================

Column {.tabset}
--------------------------------------------

**Commercial Vehicle Touring Model, Stops Models: Comparisons with Reference Scenario**

Commercial vehicle touring model output comparisons between the current scenario and the reference scenario
for the first four models in the component that simulate firm stop activity (before the set of models that simulate linking stops together into tours)

- cv_sim_activities identifies which firms make goods stops, service stops, both types of stops, or neither.
- cv_sim_schedule stops estimates the number of stops each firm makes in each TAZ as a function of firm characteristics, TAZ land use, and distance from the firm to the TAZ.
- cv_sim_scheduledstops estimates the number of stops each firm makes in each TAZ as a function of firm characteristics, TAZ land use, and distance from the firm to the TAZ. 
- cv_sim_vehicle estimates the vehicle type for each stop as a function of firm industry, distance from the firm to the TAZ, and stop activity. 
- cv_sim_stopduration estimates the length of each stop as a function of stop activity and vehicle type. 

Scenarios being compared:

- the current scenario is **`r SCENARIO_NAME`**
- the reference scenario is **`r SCENARIO_REFERENCE_NAME`**


### cv_sim_activities: Goods

```{r Chart_cv_sim_activities_industry_goods}
# Organize
dat_scen <- cv_trips[Activity %in% c("Goods", "Service"),.(Stops = .N), keyby = .(Activity, BusID)]
dat_scen <- dcast.data.table(dat_scen, BusID ~ Activity, fun.aggregate = length, value.var = "Stops")
dat_scen[, GoodsAndService := ifelse(Goods == 1 & Service == 1, 1, 0)]
dat_scen[, c("Goods", "Service") := .(ifelse(GoodsAndService == 1,0,Goods), ifelse(GoodsAndService == 1,0,Service))]
dat_scen[ScenarioFirms, Industry := i.EmpCatGroupedName, on = "BusID"]
dat_scen <- melt.data.table(dat_scen, id.vars = c("BusID", "Industry"), variable.name = "Activity", value.name = "Firms")
dat_scen <- dat_scen[, .(Firms = sum(Firms)), keyby = .(Industry, Activity)]
dat_scen <- rbind(dat_scen,
                  ScenarioFirms[!BusID %in% unique(cv_trips$BusID), .(Firms = .N, Activity = "Other"), by = .(Industry = EmpCatGroupedName)])

dat_ref <- ref_cv_trips[Activity %in% c("Goods", "Service"),.(Stops = .N), keyby = .(Activity, BusID)]
dat_ref <- dcast.data.table(dat_ref, BusID ~ Activity, fun.aggregate = length, value.var = "Stops")
dat_ref[, GoodsAndService := ifelse(Goods == 1 & Service == 1, 1, 0)]
dat_ref[, c("Goods", "Service") := .(ifelse(GoodsAndService == 1,0,Goods), ifelse(GoodsAndService == 1,0,Service))]
dat_ref[ref_ScenarioFirms, Industry := i.EmpCatGroupedName, on = "BusID"]
dat_ref <- melt.data.table(dat_ref, id.vars = c("BusID", "Industry"), variable.name = "Activity", value.name = "Firms")
dat_ref <- dat_ref[, .(Firms = sum(Firms)), keyby = .(Industry, Activity)]
dat_ref <- rbind(dat_ref,
                  ref_ScenarioFirms[!BusID %in% unique(cv_trips$BusID), .(Firms = .N, Activity = "Other"), by = .(Industry = EmpCatGroupedName)])

# Combine
dat <- rbind(dat_scen[, Source := SCENARIO_NAME], dat_ref[, Source := SCENARIO_REFERENCE_NAME])
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]
dat[, PctFirms := Firms/sum(Firms), by = .(Industry, Source)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_activities_industry.csv"))
assign("db_tab_cv_sim_activities_industry", dat, envir = db_inputs)

# Plot
bar_plotter(dat[Activity == "Goods"], xvar = "Industry", yvar = "PctFirms",  fill = "Source", position = "dodge", coord_flip = TRUE, ylabel = "Percentage of Firms", png_name = "p_cv_sim_activities_industry_goods.png")

```

### cv_sim_activities: Service

```{r Chart_cv_sim_activities_industry_service}

# Plot
bar_plotter(dat[Activity == "Service"], xvar = "Industry", yvar = "PctFirms",  fill = "Source", position = "dodge", coord_flip = TRUE, ylabel = "Percentage of Firms", png_name = "p_cv_sim_activities_industry_service.png")

```

### cv_sim_activities: Goods and Service

```{r Chart_cv_sim_activities_industry_goodsservice}

# Plot
bar_plotter(dat[Activity == "GoodsAndService"], xvar = "Industry", yvar = "PctFirms",  fill = "Source", position = "dodge", coord_flip = TRUE, ylabel = "Percentage of Firms", png_name = "p_cv_sim_activities_industry_goodsandservice.png")

```

### cv_sim_activities: No Activity

```{r Chart_cv_sim_activities_industry_other}

# Plot
bar_plotter(dat[Activity == "Other"], xvar = "Industry", yvar = "PctFirms",  fill = "Source", position = "dodge", coord_flip = TRUE, ylabel = "Percentage of Firms", png_name = "p_cv_sim_activities_industry_noactivity.png")

```

Chart Column 2 {.tabset}
--------------------------------------------

### cv_sim_scheduledstops: Industry (All Stops)

```{r Chart_cv_sim_scheduledstops_industry_all}
# Organize
dat_scen <- cv_trips[Activity %in% c("Goods", "Service"), .(Stops = .N), by = .(BusID, Activity)]
dat_scen[ScenarioFirms, Industry := i.EmpCatGroupedName, on = "BusID"]
dat_scen <- dat_scen[, .(Stops = sum(Stops)), by = .(Activity, Industry)]

dat_ref <- ref_cv_trips[Activity %in% c("Goods", "Service"), .(Stops = .N), by = .(BusID, Activity)]
dat_ref[ref_ScenarioFirms, Industry := i.EmpCatGroupedName, on = "BusID"]
dat_ref <- dat_ref[, .(Stops = sum(Stops)), by = .(Activity, Industry)]

# Combine
dat <- rbind(dat_scen[, Source := SCENARIO_NAME], dat_ref[, Source := SCENARIO_REFERENCE_NAME])
dat <- dat[, .(Stops = sum(Stops)), by = .(Industry, Source)]
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_scheduledstops_industry_all.csv"))
assign("db_tab_cv_sim_scheduledstops_industry_all", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Industry", yvar = "Stops",  fill = "Source", position = "dodge", coord_flip = TRUE, ylabel = "Number of Stops", png_name = "p_cv_sim_scheduledstops_industry_all.png")

```

### cv_sim_scheduledstops: Industry (Goods Stops)

```{r Chart_cv_sim_scheduledstops_industry_goods}
# Organize
# Combine
dat <- rbind(dat_scen[, Source := SCENARIO_NAME], dat_ref[, Source := SCENARIO_REFERENCE_NAME])
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_scheduledstops_industry_activity.csv"))
assign("db_tab_cv_sim_scheduledstops_industry_activity", dat, envir = db_inputs)

# Plot
bar_plotter(dat[Activity == "Goods"], xvar = "Industry", yvar = "Stops",  fill = "Source", position = "dodge", coord_flip = TRUE, ylabel = "Number of Stops", png_name = "p_cv_sim_scheduledstops_industry_goods.png")

```

### cv_sim_scheduledstops: Industry (Service Stops)

```{r Chart_cv_sim_scheduledstops_industry_service}
# Plot
bar_plotter(dat[Activity == "Service"], xvar = "Industry", yvar = "Stops",  fill = "Source", position = "dodge", coord_flip = TRUE, ylabel = "Number of Stops", png_name = "p_cv_sim_scheduledstops_industry_service.png")

```

### cv_sim_scheduledstops: Tabulation All Stops

```{r Table_cv_sim_scheduledstops_all}

# Organize
dat <- rbind(dat_scen[, Source := "Scenario"], dat_ref[, Source := "Reference"])
dat <- dat[, .(Stops = sum(Stops)), by = .(Industry, Source)]
dat <- add_totals(dcast.data.table(dat, Industry ~ Source, fun.aggregate = sum, value.var = "Stops"),rowtotal = FALSE)

dat[, Difference := round(Scenario - Reference)]
dat[, Ratio := round(Scenario/Reference,3)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_scheduledstops_all_tab.csv"), row.names = FALSE)
assign("db_tab_cv_sim_scheduledstops_all_tab", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") 

```

### cv_sim_scheduledstops: Tabulation Goods Stops

```{r Table_cv_sim_scheduledstops_goods}

# Organize
dat <- rbind(dat_scen[Activity == "Goods", Source := "Scenario"], dat_ref[Activity == "Goods", Source := "Reference"])
dat <- dat[, .(Stops = sum(Stops)), by = .(Industry, Source)]
dat <- add_totals(dcast.data.table(dat, Industry ~ Source, fun.aggregate = sum, value.var = "Stops"),rowtotal = FALSE)

dat[, Difference := round(Scenario - Reference)]
dat[, Ratio := round(Scenario/Reference,3)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_scheduledstops_goods_tab.csv"), row.names = FALSE)
assign("db_tab_cv_sim_scheduledstops_goods_tab", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") 

```

### cv_sim_scheduledstops: Tabulation Service Stops

```{r Table_cv_sim_scheduledstops_service}

# Organize
dat <- rbind(dat_scen[Activity == "Service", Source := "Scenario"], dat_ref[Activity == "Service", Source := "Reference"])
dat <- dat[, .(Stops = sum(Stops)), by = .(Industry, Source)]
dat <- add_totals(dcast.data.table(dat, Industry ~ Source, fun.aggregate = sum, value.var = "Stops"),rowtotal = FALSE)

dat[, Difference := round(Scenario - Reference)]
dat[, Ratio := round(Scenario/Reference,3)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_scheduledstops_service_tab.csv"), row.names = FALSE)
assign("db_tab_cv_sim_scheduledstops_service_tab", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2")

```

Chart Column 3 {.tabset}
--------------------------------------------

### cv_sim_vehicle: Activity

```{r Chart_cv_sim_vehicle_activity}
# Organize
dat_scen <- cv_trips[Activity %in% c("Goods", "Service"), .(Stops = .N), keyby = .(BusID, Vehicle, Activity)]
dat_scen[ScenarioFirms, Industry := i.EmpCatGroupedName, on = "BusID"]
dat_scen <- dat_scen[, .(Stops = sum(Stops)), by = .(Industry, Activity, Vehicle)]
dat_scen[, Activity_Vehicle := paste(Activity, Vehicle, sep = "_")]

dat_ref <- ref_cv_trips[Activity %in% c("Goods", "Service"), .(Stops = .N), keyby = .(BusID, Vehicle, Activity)]
dat_ref[ref_ScenarioFirms, Industry := i.EmpCatGroupedName, on = "BusID"]
dat_ref <- dat_ref[, .(Stops = sum(Stops)), by = .(Industry, Activity, Vehicle)]
dat_ref[, Activity_Vehicle := paste(Activity, Vehicle, sep = "_")]

# Combine
dat <- rbind(dat_scen[,.(Stops = sum(Stops)), keyby = Activity_Vehicle][, Source := SCENARIO_NAME], dat_ref[,.(Stops = sum(Stops)), keyby = Activity_Vehicle][, Source := SCENARIO_REFERENCE_NAME])
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_vehicle_activity.csv"))
assign("db_tab_cv_sim_vehicle_activity", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Activity_Vehicle", yvar = "Stops",  fill = "Source", position = "dodge", coord_flip = TRUE, ylabel = "Number of Stops", xlabel = "Activity and Vehicle", png_name = "p_cv_sim_vehicle_activity.png")

```

### cv_sim_vehicle: Tabulation Goods Stops

```{r Table_cv_sim_vehicle_goods}

# Organize
dat <- rbind(dat_scen[Activity == "Goods"][, Source := "Scenario"], dat_ref[Activity == "Goods"][, Source := "Reference"])

dat <- add_totals(dcast.data.table(dat,
                        Industry ~ Source + Vehicle,
                        fun.aggregate = sum,
                        value.var = c("Stops")),
                  rowtotal = FALSE)

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_vehicle_goods_tab.csv"), row.names = FALSE)
assign("db_tab_cv_sim_vehicle_goods_tab", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2")

```

### cv_sim_vehicle: Tabulation Service Stops

```{r Table_cv_sim_vehicle_service}

# Organize
dat <- rbind(dat_scen[Activity == "Service"][, Source := "Scenario"], dat_ref[Activity == "Service"][, Source := "Reference"])

dat <- add_totals(dcast.data.table(dat,
                        Industry ~ Source + Vehicle,
                        fun.aggregate = sum,
                        value.var = c("Stops")),
                  rowtotal = FALSE)

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_vehicle_service_tab.csv"), row.names = FALSE)
assign("db_tab_cv_sim_vehicle_service_tab", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2")

```

### cv_sim_stopduration: Good Stops

```{r Chart_cv_sim_stopduration_activity_goods}
# Organize

stop_duration_labels <- c(paste(c(1,seq(16, 91, by = 15), 151, 211, 271),
                                c(seq(15, 90, by = 15), 150, 210, 270, 390),
                                sep = "-"), "391+")

cv_trips[, duration_15min := ceiling(StopDuration / 15) * 15]

cv_trips[,
  stop_duration :=
    fcase(
      duration_15min %in% 15, 1,
      duration_15min %in% 30, 2,
      duration_15min %in% 45, 3,
      duration_15min %in% 60, 4,
      duration_15min %in% 75, 5,
      duration_15min %in% 90, 6,
      duration_15min %in% c(90 + 1:4 * 15), 7,
      duration_15min %in% c(150 + 1:4 * 15), 8,
      duration_15min %in% c(210 + 1:4 * 15), 9,
      duration_15min %in% c(270 + 1:8 * 15), 10,
      duration_15min %in% c(390 + 1:14 * 15) | duration_15min > 600, 11)]

ref_cv_trips[, duration_15min := ceiling(StopDuration / 15) * 15]

ref_cv_trips[,
  stop_duration :=
    fcase(
      duration_15min %in% 15, 1,
      duration_15min %in% 30, 2,
      duration_15min %in% 45, 3,
      duration_15min %in% 60, 4,
      duration_15min %in% 75, 5,
      duration_15min %in% 90, 6,
      duration_15min %in% c(90 + 1:4 * 15), 7,
      duration_15min %in% c(150 + 1:4 * 15), 8,
      duration_15min %in% c(210 + 1:4 * 15), 9,
      duration_15min %in% c(270 + 1:8 * 15), 10,
      duration_15min %in% c(390 + 1:14 * 15) | duration_15min > 600, 11)]

dat_scen <- cv_trips[Activity %in% c("Goods", "Service"), .(Stops = .N), keyby = .(stop_duration, Vehicle, Activity)]
dat_ref <- ref_cv_trips[Activity %in% c("Goods", "Service"), .(Stops = .N), keyby = .(stop_duration, Vehicle, Activity)]

# Combine
dat <- rbind(dat_scen[,.(Stops = sum(Stops)), keyby = .(Activity, stop_duration)][, Source := SCENARIO_NAME], dat_ref[,.(Stops = sum(Stops)), keyby = .(Activity, stop_duration)][, Source := SCENARIO_REFERENCE_NAME])
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]
dat[, stop_duration_label := stop_duration_labels[stop_duration]]
dat[, stop_duration_label := factor(stop_duration_label, levels = stop_duration_labels)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_stopduration_activity.csv"))
assign("db_tab_cv_sim_stopduration_activity", dat, envir = db_inputs)

# Plot
bar_plotter(dat[Activity == "Goods"], xvar = "stop_duration_label", yvar = "Stops",  fill = "Source", position = "dodge", ylabel = "Number of Stops", xlabel = "Stop Duration (Minutes)", png_name = "p_cv_sim_stopduration_activity_goods.png")

```

### cv_sim_stopduration: Service Stops

```{r Chart_cv_sim_stopduration_activity_service}

# Plot
bar_plotter(dat[Activity == "Service"], xvar = "stop_duration_label", yvar = "Stops",  fill = "Source", position = "dodge", ylabel = "Number of Stops", xlabel = "Stop Duration (Minutes)", png_name = "p_cv_sim_stopduration_activity_service.png")

```


### cv_sim_stopduration: Light Vehicles

```{r Chart_cv_sim_stopduration_vehicle_light}
# Organize
# Combine
dat <- rbind(dat_scen[,.(Stops = sum(Stops)), keyby = .(Vehicle, stop_duration)][, Source := SCENARIO_NAME], dat_ref[,.(Stops = sum(Stops)), keyby = .(Vehicle, stop_duration)][, Source := SCENARIO_REFERENCE_NAME])
dat[, Source := factor(Source, levels = c(SCENARIO_REFERENCE_NAME, SCENARIO_NAME))]
dat[, stop_duration_label := stop_duration_labels[stop_duration]]
dat[, stop_duration_label := factor(stop_duration_label, levels = stop_duration_labels)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_stopduration_vehicle.csv"))
assign("db_tab_cv_sim_stopduration_vehicle", dat, envir = db_inputs)

# Plot
bar_plotter(dat[Vehicle == "Light"], xvar = "stop_duration_label", yvar = "Stops",  fill = "Source", position = "dodge", ylabel = "Number of Stops", xlabel = "Stop Duration (Minutes)", xrotate = TRUE, png_name = "p_cv_sim_stopduration_vehicle_light.png")

```

### cv_sim_stopduration: Medium Trucks

```{r Chart_cv_sim_stopduration_vehicle_medium}

# Plot
bar_plotter(dat[Vehicle == "Medium"], xvar = "stop_duration_label", yvar = "Stops",  fill = "Source", position = "dodge", ylabel = "Number of Stops", xlabel = "Stop Duration (Minutes)", xrotate = TRUE, png_name = "p_cv_sim_stopduration_vehicle_medium.png")

```

### cv_sim_stopduration: Heavy Trucks

```{r Chart_cv_sim_stopduration_vehicle_heavy}

# Plot
bar_plotter(dat[Vehicle == "Heavy"], xvar = "stop_duration_label", yvar = "Stops",  fill = "Source", position = "dodge", ylabel = "Number of Stops", xlabel = "Stop Duration (Minutes)", xrotate = TRUE, png_name = "p_cv_sim_stopduration_vehicle_heavy.png")

```

Comparison Tours {data-navmenu="Commercial Vehicle Touring Model"}
============================================

Column {.tabset}
--------------------------------------------

**Commercial Vehicle Touring Model, Tour Models: Comparison with Reference Sceario**

Commercial vehicle touring model comparisons between the current scenario and the reference scenario for the last three models in the component that simulate tours

- cv_sim_tours identifies the group of stops to form each tour, the tour type, and the sequence of stops in the tour.
- cv_sim_scheduletrips simulates the arrival time at the first stop on the tour and based on that, stop durations, and trip travel times, calculates the depature and arrival time of every trip in the tour.
- cv_sim_intermediatestops estimates whether each trip includes an intermediate stop (e.g., for vehicle servicing or driver needs) and if so, how long that stop takes and whether that stop is located. All tours are retimed to account for intermediate stops.

Scenarios being compared:

- the current scenario is **`r SCENARIO_NAME`**
- the reference scenario is **`r SCENARIO_REFERENCE_NAME`**

### cv_sim_tours: Light Vehicles

```{r Chart_cv_sim_tours_light}
# Organize
dat_scen <- cv_trips[TripID == 1, .(Tours = .N), keyby = .(TourType, Vehicle)]
dat_ref <- ref_cv_trips[TripID == 1, .(Tours = .N), keyby = .(TourType, Vehicle)]
dat <- rbind(dat_scen[, Source := SCENARIO_NAME], dat_ref[, Source := SCENARIO_REFERENCE_NAME])
dat[, NumStops := ifelse(substr(TourType,3,3) == "s", "Single", "Multiple")]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_tours_type_vehicle.csv"))
assign("db_tab_cv_sim_tours_type_vehicle", dat, envir = db_inputs)

# Plot
dat[, Stops_Type := paste(NumStops, toupper(TourType), sep = "_")]
bar_plotter(dat[Vehicle == "Light"], xvar = "Stops_Type", yvar = "Tours",  fill = "Source", position = "dodge", coord_flip = TRUE, ylabel = "Number of Tours", png_name = "p_cv_sim_tours_type_vehicle_light.png")

```

### cv_sim_tours: Medium Trucks

```{r Chart_cv_sim_tours_medium}

# Plot
bar_plotter(dat[Vehicle == "Medium"], xvar = "Stops_Type", yvar = "Tours",  fill = "Source", position = "dodge", coord_flip = TRUE, ylabel = "Number of Tours", png_name = "p_cv_sim_tours_type_vehicle_medium.png")

```

### cv_sim_tours: Heavy Trucks

```{r Chart_cv_sim_tours_heavy}

# Plot
bar_plotter(dat[Vehicle == "Heavy"], xvar = "Stops_Type", yvar = "Tours",  fill = "Source", position = "dodge", coord_flip = TRUE, ylabel = "Number of Tours", png_name = "p_cv_sim_tours_type_vehicle_heavy.png")

```


Chart Column 2 {.tabset}
--------------------------------------------

### cv_sim_scheduledtrips: Arrival Time (All Tours)

```{r Chart_cv_sim_scheduledtrips}
# Organize
dat_scen <- cv_trips[TripID == MinTripID, .(Tours = .N), keyby = .(Vehicle, Hour = floor(as.numeric(MAMArrive)/60))]
dat_ref <- ref_cv_trips[TripID == MinTripID, .(Tours = .N), keyby = .(Vehicle, Hour = floor(as.numeric(MAMArrive)/60))]
dat <- rbind(dat_scen[, .(Tours = sum(Tours)), keyby = Hour][, Source := SCENARIO_NAME], dat_ref[, .(Tours = sum(Tours)), keyby = Hour][, Source := SCENARIO_REFERENCE_NAME])
dat[, Hour := factor(Hour)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_scheduledtrips_all.csv"))
assign("db_tab_cv_sim_scheduledtrips_all", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "Hour", yvar = "Tours",  fill = "Source", position = "dodge", ylabel = "Number of Tours", png_name = "p_cv_sim_scheduledtrips_all.png", xrotate = TRUE)

```

### cv_sim_scheduledtrips: Arrival Time (Light Vehicles)

```{r Chart_cv_sim_scheduledtrips_light}
# Organize
dat <- rbind(dat_scen[, Source := SCENARIO_NAME], dat_ref[, Source := SCENARIO_REFERENCE_NAME])
dat[, Hour := factor(Hour)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_scheduledtrips_vehicle.csv"))
assign("db_tab_cv_sim_scheduledtrips_vehicle", dat, envir = db_inputs)

# Plot
bar_plotter(dat[Vehicle == "Light"], xvar = "Hour", yvar = "Tours",  fill = "Source", position = "dodge", ylabel = "Number of Tours", png_name = "p_cv_sim_scheduledtrips_light.png", xrotate = TRUE)

```

### cv_sim_scheduledtrips: Arrival Time (Medium Trucks)

```{r Chart_cv_sim_scheduledtrips_medium}

# Plot
bar_plotter(dat[Vehicle == "Medium"], xvar = "Hour", yvar = "Tours",  fill = "Source", position = "dodge", ylabel = "Number of Tours", png_name = "p_cv_sim_scheduledtrips_medium.png", xrotate = TRUE)

```

### cv_sim_scheduledtrips: Arrival Time (Heavy Trucks)

```{r Chart_cv_sim_scheduledtrips_heavy}

# Plot
bar_plotter(dat[Vehicle == "Heavy"], xvar = "Hour", yvar = "Tours",  fill = "Source", position = "dodge", ylabel = "Number of Tours", png_name = "p_cv_sim_scheduledtrips_heavy.png", xrotate = TRUE)

```

Chart Column 3 {.tabset}
--------------------------------------------

### cv_sim_intermediatestops: Stop Type (All)

```{r Chart_cv_sim_intermediatestops}
# Organize
dat_scen <- cv_trips[Activity %in% c("Break/Meal", "Vehicle Service", "Other"), .(Stops = .N), keyby = .(StopType = Activity, Vehicle)]
dat_ref <- ref_cv_trips[Activity %in% c("Break/Meal", "Vehicle Service", "Other"), .(Stops = .N), keyby = .(StopType = Activity, Vehicle)]
dat <- rbind(dat_scen[, .(Stops = sum(Stops)), keyby = StopType][, Source := SCENARIO_NAME], dat_ref[, .(Stops = sum(Stops)), keyby = StopType][, Source := SCENARIO_REFERENCE_NAME])

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_intermediatestops_all.csv"))
assign("db_tab_cv_sim_intermediatestops_all", dat, envir = db_inputs)

# Plot
bar_plotter(dat, xvar = "StopType", yvar = "Stops",  fill = "Source", position = "dodge", ylabel = "Number of Stops", png_name = "p_cv_sim_intermediatestops_all.png", xrotate = TRUE)

```

### cv_sim_intermediatestops: Stop Type (Light Vehicles)

```{r Chart_cv_intermediatestops_light}
# Organize
dat <- rbind(dat_scen[, Source := SCENARIO_NAME], dat_ref[, Source := SCENARIO_REFERENCE_NAME])

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "cv_sim_intermediatestops_vehicle.csv"))
assign("db_tab_cv_sim_intermediatestops_vehicle", dat, envir = db_inputs)

# Plot
bar_plotter(dat[Vehicle == "Light"], xvar = "StopType", yvar = "Stops",  fill = "Source", position = "dodge", ylabel = "Number of Stops", png_name = "p_cv_sim_intermediatestops_light.png", xrotate = TRUE)

```

### cv_sim_intermediatestops: Stop Type (Medium Trucks)

```{r Chart_cv_intermediatestops_medium}

# Plot
bar_plotter(dat[Vehicle == "Medium"], xvar = "StopType", yvar = "Stops",  fill = "Source", position = "dodge", ylabel = "Number of Stops", png_name = "p_cv_sim_intermediatestops_medium.png", xrotate = TRUE)

```

### cv_sim_intermediatestops: Stop Type (Heavy Trucks)

```{r Chart_cv_intermediatestops_heavy}

# Plot
bar_plotter(dat[Vehicle == "Heavy"], xvar = "StopType", yvar = "Stops",  fill = "Source", position = "dodge", ylabel = "Number of Stops", png_name = "p_cv_sim_intermediatestops_heavy.png", xrotate = TRUE)

```

