---
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: yeti
    css: "ReportDashboardStyles.css"
editor_options: 
  chunk_output_type: console
---
Comparison {data-navmenu="Trip Tables"}
============================================

Highlights {data-width=300}
--------------------------------------------

**Trip Tables: Comparison with Reference Scenario**

Daily trip table summaries, comparing trip table characteristics such as county to county OD patterns between the current scenario and the reference scenario.

Scenarios being compared:

- the current scenario is **`r SCENARIO_NAME`**
- the reference scenario is **`r SCENARIO_REFERENCE_NAME`**

### VMT Comparison

```{r Chart_tt_comp_vmt_tab}
# Organize

dat <- ref_tmh_vtods[,.(Reference = sum(VMT)), keyby = .(Vehicle)]

dat[tmh_vtods[,.(Scenario = sum(VMT)), keyby = .(Vehicle)],
    Scenario := i.Scenario, on = "Vehicle"]

dat[, Difference := Scenario - Reference]

dat <- add_totals(dat, rowtotal = FALSE)                  

dat[, Ratio := Scenario/Reference]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "tt_build_comp_vmt_tab.csv"))
assign("db_tab_tt_build_comp_vmt_tab", dat, envir = db_inputs)

# Table
cols <- names(dat)[2:(ncol(dat)-1)]
dat[, (cols) := lapply(.SD, format, digits = 0, big.mark = ",", scientific = FALSE), .SDcols = cols]

kable(dat, escape=FALSE, digits = 3) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed"))  %>%
  row_spec(nrow(dat), background = "#f2f2f2")

```

### Trip Table Comparison Summary

```{r Chart_tt_comp_summary_tab}
# Organize
# summary/mean values in a table with measure, model, target

# average trip distance
# average tour distance
# average tour time
# average stops per tour (excluding return stop)
# percent single stop tours (vs multistop)
# average base to stop distance
# average cluster distance
# average stop duration

# Create the reference portion of the table and then add observed data
# Create from the ref_cv_trips table in case validation summaries not available
dat <- data.table(Field = c("Trips: Distance", "Tours: Distance", "Tours: Number of Stops (Excluding Return to Base)",
                             "Tours: Single Stop Tours (vs. Multi-Stop)", "Trips: Base-to-StopDistance",
                             "Tours: Cluster Distance", "Trips: Stop Duration", "Tours: Tour Duration"),
                  Statistic = c("Mean (Miles)", "Mean (Miles)", "Mean (# Stops)",
                                "Proportion", "Mean (Miles)", "Mean (Miles)",
                                "Mean (Minutes)", "Mean (Minutes)"))

dat[Field == "Trips: Distance", Reference := round(mean(ref_cv_trips$Distance, na.rm = TRUE), 2)]
dat[Field == "Tours: Distance", Reference := round(mean(ref_cv_trips[,.(Distance = sum(Distance)), by = TourID]$Distance),2)]
dat[Field == "Tours: Number of Stops (Excluding Return to Base)", Reference := round(mean(ref_cv_trips[Activity != "Return",.(NumStops = .N), by = TourID]$NumStops),2)]
dat[Field == "Tours: Single Stop Tours (vs. Multi-Stop)", Reference := round((ref_cv_trips[Activity != "Return",.N,by = TourID][N==1,.N])/uniqueN(cv_trips$TourID),2)]
dat[Field == "Trips: Base-to-StopDistance", Reference := round(mean(ref_cv_trips[Activity != "Return"]$Distance.Start),2)]
dat[Field == "Tours: Cluster Distance", Reference := round(mean(ref_cv_trips_cluster$MeanDist),2)]
dat[Field == "Trips: Stop Duration", Reference := round(mean(ref_cv_trips[Activity != "Return"]$StopDuration),2)]
dat[Field == "Tours: Tour Duration", Reference := round(mean(ref_cv_trips[,.(TourDuration = sum(TravelTime, StopDuration)), by = TourID]$TourDuration),2)]

dat[Field == "Trips: Distance", Scenario := round(mean(cv_trips$Distance, na.rm = TRUE), 2)]
dat[Field == "Tours: Distance", Scenario := round(mean(cv_trips[,.(Distance = sum(Distance)), by = TourID]$Distance),2)]
dat[Field == "Tours: Number of Stops (Excluding Return to Base)", Scenario := round(mean(cv_trips[Activity != "Return",.(NumStops = .N), by = TourID]$NumStops),2)]
dat[Field == "Tours: Single Stop Tours (vs. Multi-Stop)", Scenario := round((cv_trips[Activity != "Return",.N,by = TourID][N==1,.N])/uniqueN(cv_trips$TourID),2)]
dat[Field == "Trips: Base-to-StopDistance", Scenario := round(mean(cv_trips[Activity != "Return"]$Distance.Start),2)]
dat[Field == "Tours: Cluster Distance", Scenario := round(mean(cv_trips_cluster$MeanDist),2)]
dat[Field == "Trips: Stop Duration", Scenario := round(mean(cv_trips[Activity != "Return"]$StopDuration),2)]
dat[Field == "Tours: Tour Duration", Scenario := round(mean(cv_trips[,.(TourDuration = sum(TravelTime, StopDuration)), by = TourID]$TourDuration),2)]

dat[, Difference := Scenario - Reference]
dat[, Ratio := Scenario/Reference]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "tt_build_comp_summary_tab.csv"))
assign("db_tab_tt_build_comp_summary_tab", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE, digits = 3) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) 

```


Column {data-width=500, .tabset}
--------------------------------------------

### District Origins (All Vehicles) 

```{r Chart_tt_comp_District_origins}
# Organize
dat_scen <- TripTable[, .(ScenTrips = sum(trips, na.rm = TRUE)), keyby = .(OriginDistrict = OSummaryGeog)]
dat_scen[, Scenario := ScenTrips/sum(ScenTrips)]

dat_ref <- ref_TripTable[, .(RefTrips = sum(trips, na.rm = TRUE)), keyby = .(OriginDistrict = OSummaryGeog)]
dat_ref[, Reference := RefTrips/sum(RefTrips)]


dat <- merge(dat_ref, dat_scen, by= "OriginDistrict", all = TRUE)
dat[is.na(Reference), Reference := 0]
dat[is.na(Scenario), Scenario := 0]

dat[, Difference := Scenario - Reference]
dat[, Ratio := ifelse(Reference != 0, Scenario/Reference, 0)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "tt_build_district_origins_all.csv"))
assign("db_tab_tt_build_district_origins_all", dat, envir = db_inputs)

# Table
kable(dat[,.(OriginDistrict, Reference, Scenario, Difference, Ratio)], escape=FALSE, digits = 3) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) 

```


### District Destinations (All Vehicles) 

```{r Chart_tt_comp_District_dest}
# Organize
dat_scen <- TripTable[, .(ScenTrips = sum(trips, na.rm = TRUE)), keyby = .(DestinationDistrict = DSummaryGeog)]
dat_scen[, Scenario := ScenTrips/sum(ScenTrips)]

dat_ref <- ref_TripTable[, .(RefTrips = sum(trips, na.rm = TRUE)), keyby = .(DestinationDistrict = DSummaryGeog)]
dat_ref[, Reference := RefTrips/sum(RefTrips)]

dat <- merge(dat_ref, dat_scen, by= "DestinationDistrict", all = TRUE)
dat[is.na(Reference), Reference := 0]
dat[is.na(Scenario), Scenario := 0]

dat[, Difference := Scenario - Reference]
dat[, Ratio := ifelse(Reference != 0, Scenario/Reference, 0)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "tt_build_district_dest_all.csv"))
assign("db_tab_tt_build_district_origins_all", dat, envir = db_inputs)

# Table
kable(dat[,.(DestinationDistrict, Reference, Scenario, Difference, Ratio)], escape=FALSE, digits = 3) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) 

```

### District Origins (Light Vehicles) 

```{r Chart_tt_comp_District_origins_light}
# Organize
dat_scen <- TripTable[, .(ScenTrips = sum(trips, na.rm = TRUE)), keyby = .(OriginDistrict = OSummaryGeog, Vehicle)]
dat_scen[, Scenario := ScenTrips/sum(ScenTrips), by = Vehicle]

dat_ref <- ref_TripTable[, .(RefTrips = sum(trips, na.rm = TRUE)), keyby = .(OriginDistrict = OSummaryGeog, Vehicle)]
dat_ref[, Reference := RefTrips/sum(RefTrips), by = Vehicle]


dat <- merge(dat_ref, dat_scen, by= c("OriginDistrict", "Vehicle"), all = TRUE)
dat[is.na(Reference), Reference := 0]
dat[is.na(Scenario), Scenario := 0]

dat[, Difference := Scenario - Reference]
dat[, Ratio := ifelse(Reference != 0, Scenario/Reference, 0)]

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "tt_build_district_origins_vehicle.csv"))
assign("db_tab_tt_build_district_origins_vehicle", dat, envir = db_inputs)

# Table
kable(dat[Vehicle == "Light",.(OriginDistrict, Reference, Scenario, Difference, Ratio)], escape=FALSE, digits = 3) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) 

```

### District Origins (Medium Trucks) 

```{r Chart_tt_comp_District_origins_medium}
# Table
kable(dat[Vehicle == "Medium",.(OriginDistrict, Reference, Scenario, Difference, Ratio)], escape=FALSE, digits = 3) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) 

```

### District Origins (Heavy Trucks) 

```{r Chart_tt_val_District_origins_heavy}
# Table
kable(dat[Vehicle == "Heavy",.(OriginDistrict, Reference, Scenario, Difference, Ratio)], escape=FALSE, digits = 3) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) 

```


### Percent Trips by District OD: Scenario

```{r Chart_Percent_Trips_By_District_OD_scen}
# Organize
dat_scen <- TripTable[, .(ScenTrips = sum(trips, na.rm = TRUE)), by = .(OriginDistrict = OSummaryGeog, DestinationDistrict = DSummaryGeog)]
dat_scen[, Scenario := ScenTrips/sum(ScenTrips)]
dat <- add_totals(dcast.data.table(dat_scen,
                                  OriginDistrict ~ DestinationDistrict,
                                   fun.aggregate = sum,
                                   value.var = "Scenario"))

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "tt_build_district_od_scen.csv"))
assign("db_tab_tt_build_district_od_scen", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE, digits = 3) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```

### Percent Trips by District OD: Reference

```{r Chart_Percent_Trips_By_District_OD_ref}
# Organize
dat_ref <- ref_TripTable[, .(RefTrips = sum(trips, na.rm = TRUE)), by = .(OriginDistrict = OSummaryGeog, DestinationDistrict = DSummaryGeog)]
dat_ref[, Reference := RefTrips/sum(RefTrips)]
dat <- add_totals(dcast.data.table(dat_ref,
                                  OriginDistrict ~ DestinationDistrict,
                                   fun.aggregate = sum,
                                   value.var = "Reference"))

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "tt_build_District_od_ref.csv"))
assign("db_tab_tt_build_district_od_ref", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE, digits = 3) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed")) %>%
  row_spec(nrow(dat), background = "#f2f2f2") %>%
  column_spec(ncol(dat), background = "#f2f2f2")

```


### Percent Trips by District OD: Difference (Scenario - Reference)

```{r Chart_Percent_Trips_By_District_OD_diff}
# Organize
dat_diff <- merge(dat_ref, dat_scen, by = c("OriginDistrict", "DestinationDistrict"))
dat_diff[, Difference := Scenario - Reference]

dat <- dcast.data.table(dat_diff,
       OriginDistrict ~ DestinationDistrict,
       fun.aggregate = sum,
       value.var = "Difference")

# Save
fwrite(dat, file = file.path(SCENARIO_OUTPUT_PATH, "tt_build_district_od_comp_diff.csv"))
assign("db_tab_tt_build_district_od_comp_diff", dat, envir = db_inputs)

# Table
kable(dat, escape=FALSE, digits = 3) %>%
  kable_styling(fixed_thead = TRUE, bootstrap_options = c("condensed"))

```

